Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-10-15 analysis/paper/paper.qmd
finish editing introduction

To understand the role stemmed points played in the technological transition, this study examines the functions of stemmed points. We use the tip cross-sectional area (TCSA) metric to calculate artifact function and compare the results to other archaeological and ethnographic assemblages based on the idea that different shapes correspond to different functions [@lombard2021variation]. We then explore the relationship between and function raw materials, artifact size and discard location, and how these change over time. Our main questions are: What were stemmed points used for? How diverse were their functions? What are the temporal patterns in stemmed point functions? As part of our discussion, we examine possible connections between the roles of stemmed points and population dynamics or environmental change during the Late Paleolithic period. In order to understand how a certain weapon-tip type was chosen, we purposely borrow evolutionary perspective and premise that human groups had the cognitive capacity to choose proper weapons depending on their hunting strategies and socio-environmental circumstances.

>>>>

To understand the likely roles that stemmed points played in the technological transition, this study examines the possible uses of stemmed points. We use the tip cross-sectional area (TCSA) metric to infer likely artifact use, and compare the results to other archaeological and ethnographic assemblages based on the idea that different shapes correspond to different weapon types [@lombard2021variation]. We then explore the relationship between likely use and raw materials, artifact size and discard location, and how these change over time. Our main questions are: What was the best-fit ballistic probability for the stemmed points if they were hafted as weapon tips? How diverse were their likely uses? What are the temporal patterns in stemmed point uses? As part of our discussion, we examine possible connections between the roles of stemmed points and population dynamics or environmental change during the Late Paleolithic period. In order to understand how a certain weapon-tip type was chosen, we apply an evolutionary perspective with the assumption that people chose their weapon tip types depending on their hunting strategies and socio-environmental circumstances.
